Smart Drill-Down: Interactive Summarization of Relational Tables

### 2014-11-21 TableSummarization/Paper/exp.tex
New graphs. Yet to be added to writeup

>>>>

\begin{comment}
more experiment stuff
vanilla a priori size scoring, first 7 columns (maybe we should include 13, to show suffering on english rule
Female & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2940$ & $2$ \\
$\star$ & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $5182$ & $1$ \\
Female & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4918$ & $1$ \\
Male & $\star$ & $\star$ & $\star$ & $\star$ & > 10 years & $2242$ & $2$ \\
$\star$ & Married & $\star$ & $\star$ & $\star$ & > 10 years & $2053$ & $2$ \\
Male & $\star$ & $\star$ & $\star$ & $\star$ & $\star$ & $4075$ & $1$ \\
Female & Married & $\star$ & $\star$ & $\star$ & $\star$ & $1966$ & $2$ \\
$\star$ & Never married & $\star$ & $\star$ & $\star$ & > 10 years & $1964$ & $2$ \\

\end{comment}
